Hippocampal replay of experience at real world speeds

### 2021-05-13 Article.tex
Update on Overleaf.

We hypothesize that this large set of events supports the ability to store and update  representations of individual places and snippets of experience. Previous findings demonstrated that SWRs with movement- or immobility-related activity engage specific patterns of spiking activity outside the hippocampus \citep{YuDistincthippocampalcorticalmemory2017, JadhavCoordinatedExcitationInhibition2016}. Thus, we would expect that the large set of events with slow dynamics would also engage specific patterns of activity outside the hippocampus, perhaps allowing animals to store or update the value of specific locations or short movement trajectories without having to generate full trajectories representing one of multiple ways to arrive at a location \citep{YuHippocampalcorticalinteraction2015}. Events that contain multiple dynamics (e.g. two continuous representations separated by a brief fragmented representation) might also help bind together experiences that occur in the same environment but at different places. Alternatively, it might be that downstream structures are attuned to these dynamics, and that each period of coherent hippocamapal dynamics drives its own set of responses elsewhere in the brain. We further note that recent results from a study of activity patterns during movement indicates that individual theta cycles can have different dynamics as well (CITE Pfeiffer paper), suggesting that the underlying sequences seen during replay and theta may overlap in their content and dynamics.

Simiarly, it is possible that slow and fast dynamics are supported by different subcircuits. \cite{YamamotoDirectMedialEntorhinal2017} found that blocking medial entorhinal cortex (MEC) output to CA1 resulted in shorter (and therefore slower) replay trajectories and \cite{OlivaOriginGammaFrequency2018} showed that layer 2/3 MEC neurons increased their firing 50 ms before the start of longer duration SWRs (>100 ms). This raises the possibility that these slower replays are driven by CA3-CA1 interaction while the faster trajectories are more externally driven by MEC-CA1, and that these different events could also engage different circuits outside of the hippocampus and entorhinal cortex.

>>>>

We hypothesize that this large set of events supports the ability to store and update  representations of individual places and snippets of experience. Previous findings demonstrated that SWRs with movement- or immobility-related activity engage specific patterns of spiking activity outside the hippocampus \citep{YuDistincthippocampalcorticalmemory2017, JadhavCoordinatedExcitationInhibition2016}. Thus, we would expect that the large set of events with slow dynamics would also engage specific patterns of activity outside the hippocampus, perhaps allowing animals to store or update the value of specific locations or short movement trajectories without having to generate full trajectories representing one of multiple ways to arrive at a location \citep{YuHippocampalcorticalinteraction2015}. Events that contain multiple dynamics (e.g. two continuous representations separated by a brief fragmented representation) might also help bind together experiences that occur in the same environment but at different places. Alternatively, it might be that downstream structures are attuned to these dynamics, and that each period of coherent hippocamapal dynamics drives its own set of responses elsewhere in the brain. We further note that recent results from a study of activity patterns during movement indicates that individual theta cycles can have different dynamics as well \citep{WangAlternatingsequencesfuture2020}, suggesting that the underlying sequences seen during replay and theta may overlap in their content and dynamics.

Similarly, it is possible that slow and fast dynamics are supported by different subcircuits. \cite{YamamotoDirectMedialEntorhinal2017} found that blocking medial entorhinal cortex (MEC) output to CA1 resulted in shorter (and therefore slower) replay trajectories and \cite{OlivaOriginGammaFrequency2018} showed that layer 2/3 MEC neurons increased their firing 50 ms before the start of longer duration SWRs (>100 ms). This raises the possibility that these slower replays are driven by CA3-CA1 interaction while the faster trajectories are more externally driven by MEC-CA1, and that these different events could also engage different circuits outside of the hippocampus and entorhinal cortex.
